---
title: ShinySoils
output: html_document
runtime: shiny
---

# ShinySoils -- practical tools for the soil science laboratory  

*kaizadp - 2023*

---

<style>
  .nav-pills>li>a {
     color: black;
      background-color: #a0c4ff
     }
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     color: white;
     background-color: #023e8a;
     }

</style>


```{r, eval = FALSE, echo=FALSE}
# CSS styling for tabs
<style>
  .nav-pills>li>a {
     color: pink;
     }
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     color: black;
     background-color: red;
     }
  .nav-pills > li:nth-of-type(2)>a {
     color: green;
     }
  .nav-pills > li:nth-of-type(2)>a:hover, .nav-pills > li:nth-of-type(2)>a:focus, .nav-pills > li:nth-of-type(2).active>a {
     color: black;
     background-color: green;
     }
</style>
```

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### {.tabset .tabset-fade .tabset-pills}

#### Welcome

***

Welcome to `ShinySoils`. 

This Shiny App contains basic tools for soil science calculations.

This is still a work in progress, and more tools will be added in due time. 

If you have suggestions or comments, please use the `Issues` tab in the [GitHub repository](https://github.com/kaizadp/shinysoils). 

***

**Kaizad F. Patel - created Aug 2020**  

Last updated: `r Sys.Date()`

Made using ShinyApps  
Code available on [GitHub](https://github.com/kaizadp/shinysoils)  
Twitter: [kaiz_p](https://twitter.com/kaiz_p)



#### Soil Water Suction
```{r}
source("soilwatersuction.R")

shinyApp(ui = ui, server = server)

```




#### Stable Isotopes

***

Use this handy units converter for ^13^C and ^15^N stable isotopes.

***

```{r}
source("isotopes.R")
```

##### {.tabset .tabset-fade .tabset-pills }

###### Carbon


***

<div class = "row">
  
<div class = "col-md-4">

**convert from R**

```{r}
shinyApp(ui = carbon_from_r()$ui, server = carbon_from_r()$server)
```

</div>
  
<div class = "col-md-4">

**convert from F**

```{r}
shinyApp(ui = carbon_from_f()$ui, server = carbon_from_f()$server)
```
</div>

  
<div class = "col-md-4">

**convert from δ**

```{r}
shinyApp(ui = carbon_from_d()$ui, server = carbon_from_d()$server)
```

</div>
</div>



###### Nitrogen

***

<div class = "row">
  
<div class = "col-md-4">

**convert from R**

```{r}
shinyApp(ui = nitrogen_from_r()$ui, server = nitrogen_from_r()$server)
```

</div>
  
<div class = "col-md-4">

**convert from F**

```{r}
shinyApp(ui = nitrogen_from_f()$ui, server = nitrogen_from_f()$server)
```
</div>

  
<div class = "col-md-4">

**convert from δ**

```{r}
shinyApp(ui = nitrogen_from_d()$ui, server = nitrogen_from_d()$server)
```

</div>
</div>

###### Mixing model

***

Two pool mixing model, to determine the enrichment of a mixture, given the enrichments of two sources.

You can use R or δ for the calculations, but keep it consistent.

```{r}
shinyApp(ui = mixing_model()$ui, server = mixing_model()$server)
```

###### Calculations

Notations and Calculations

***

**fractional abundance (F)**

$F = \frac{heavy}{heavy + light}$

$F^{13}C = \frac{^{13}C}{^{13}C + ^{12}C}$

$F^{15}N = \frac{^{15}N}{^{15}N + ^{14}N}$

<br>


**atom percent (at%)**

$at = F * 100$

$at^{13}C = (\frac{^{13}C}{^{13}C + ^{12}C}) * 100$

<br>


**isotope ratio (R)**

$R = \frac{heavy}{light}$

$^{13}R = \frac{^{13}C}{^{12}C}$

$^{15}R = \frac{^{15}N}{^{14}N}$

<br>


$^{13}R = \frac{^{13}F}{(1 - ^{13}F)}$

$^{13}F = \frac{^{13}R}{(1 + ^{13}R)}$

<br>


**delta (δ)** *units permil, ‰*

$δ = \frac{R_{sample}}{R_{standard} - 1} * 1000$

$δ^{13}C = \frac{^{13}R_{sample}}{^{13}R_{VPDB} - 1} * 1000$

<br>


**to calculate the enrichment of a mixture** *two pool mixing model*

$Mass_{mixture} * R_{mixture} = (Mass_1 * R_1) + (Mass_2 * R_2)$

$Mass_{mixture} * δ_{mixture} = (Mass_1 * δ_1) + (Mass_2 * δ_2)$





###### Standard values

***

- **Vienna-PeeDee Belemnite (VPDB)** ^13^C/^12^C = 0.011180


- **Air** ^15^N/^14^N = 0.0036765


```{r, eval=FALSE}
library(tibble)

standards = 
  tribble(
    ~standard , ~ratio, ~value,
    "Vienna PDB", "13C/12C", 0.0036765
  )

standards %>%
  knitr::kable("simple")
```




###### Old app


```{r}
source("isotopes.R")

shinyApp(ui = ui, server = server)
```



